### 2019-02-26 manuscript.tex
Update manuscript.tex

The main response variables were woman's intention to cut their daughters in the daughter model and the daughter-future model, and woman's attitude on whether FGC should be continued in the FGC future model.  The main predictors were beliefs of FGC benefits, woman's FGC status and attitudes of gender equality.  Other socio demographic variables were also included:  age, education, religion (see the list of religion recode at table xx in appendix; with a footnote on how we recoded it), marital status, work status, media and residence (urban vs. rural) in addition to country.  The followings were treated as random variables:  cluster ID (villages) and ethnicity (see the list of ethnicity recode at table xx in appendix; with a footnote on how we recoded it).

@@

Baseline socio-demographic and sample characteristics are shown in xxx.  The prevalence of FGC are \%, \%, \% and \% in Kenya, Mali, Nigeria and Sierra Leon accordingly.

>>>>

The main response variables were woman's intention to cut their daughters in the daughter model and the daughter-future model, and woman's attitude on whether FGC should be continued in the FGC future model.  The main predictors were woman's FGC status, beliefs of FGC benefits and attitudes of gender equality.  Other socio demographic variables were also included:  age, education, religion (see the list of religion recode at table xx in appendix; with a footnote on how we recoded it), marital status, work status, media and residence (urban vs. rural) in addition to country.  The followings were treated as random variables:  cluster ID (villages) and ethnicity (see the list of ethnicity recode at table xx in appendix; with a footnote on how we recoded it).

@@

Baseline socio-demographic and sample characteristics are shown in xxx.  The prevalence of FGC are \%, \%, \% and \% in Kenya, Mali, Nigeria and Sierra Leon accordingly, and \%, \%, \% and \%  of the samples thought FGC should continue as well.

The results of the three models are at ____.  The findings showed that all the three responses were clearly associated with the following predictors:  women’s fgc status, beliefs of fgc benefits and community level of women’s fgc status; so as the following factors:  country, media, education, age and religion and the community levels of media, education.  We did not find clear association of the community level of beliefs of fgc benefits and the three responses.

\cfcmt{main predictors:  beliefs of FGC benefits, woman's FGC status and attitudes of gender equality}
